The Actions We Compute are Not Invariant

### 2018-12-03 paper/ms.tex
Update paper

@@

\section{Optimally Axisymmetric Frame}
An analytic, axisymmetric potential with a known reference frame is a far too
simple description of the Milky Way. We thus turn to cosmological zoom-in
simulations as approximations to a ``true'' Milky Way potential. It is important to remember that

\subsection{Cosmological Zoom-in} \label{ssec:cosmozoom}
Cosmological zoom-ins allow one to simulate a selected region at high resolution embedded in a low-resolution cosmological background \citep[e.g.][]{1993ApJ...412..455K,2014MNRAS.437.1894O}

\subsection{Cluster Simulations} \label{ssec:cluster_sim}

\appendix \section{Pattern Speed} Our estimation of the pattern speed is very
crude, but throughout the text we have adopted three different speeds in
order to demonstrate that qualitatively our results do not depend on the
precise numerical value of the pattern speed. We identify the spiral arms by
first plotting a $\phi$-$R$ 2D histogram, shown in
Figure~\ref{fig:pattern_speed}. In order to compute $\phi$ and $R$, we use
the principal axes from \citep{2018arXiv180610564S}. Push push

\begin{figure}
\centering
\includegraphics[width=\textwidth,height=\textheight,keepaspectratio]{{pattern_speed_by_eye}.png}
\caption{Pattern speed.}
\label{fig:pattern_speed}
\end{figure}

>>>>

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\z}{z}

@@

\section{Optimally Axisymmetric Frame}
An analytic, axisymmetric potential with a known reference frame is a far too
simple description of the Milky Way. We thus turn to cosmological zoom-in
simulations as approximations to a ``true'' Milky Way potential. We will perform a few simulations of small clusters in order to

\subsection{Cosmological Zoom-in} \label{ssec:cosmozoom}
Cosmological zoom-ins allow one to simulate a selected region at high
resolution embedded in a low-resolution cosmological background
\citep[e.g.][]{1993ApJ...412..455K,2014MNRAS.437.1894O}. Here we use a
zoom-in of a Milky Way-mass galaxy from the FIRE-2 collaboration.

First, a dark matter only simulation was run with $\Lambda$CDM cosmology
parameterized by $(\Omega_m, \Omega_{\Lambda}, \Omega_b, h, \sigma_8, n_s) =
(0.272, 0.728, 0.0455, 0.702, 0.807, 0.961)$, consistent with current
constraints \citep{2018arXiv180706209P}. Halos are selected at $z=0$ based
solely on their mass ($\sim 1\text{--}2 \times 10^{12} \Msun$). Particles
within $5 R_{200\text{m}}$ of each halo are traced back to $\z=99$ and the
initial conditions are regenerated at higher resolution using MUSIC
\citep{2011MNRAS.415.2101H}. A total of $\sim 10$ halos were simulated at
higher resolution \citep{2018MNRAS.481.4133G}.

These halos are uncontaminated and contain gas particles of mass $\sim 7000
\text{--} 20000 \Msun$ and star particles of mass $\sim 5000 \text{--} 7000
\Msun$, with the lower end coming from stellar evolution
\citep{2018arXiv180610564S}. Softening lengths for dark matter and star
particles are fixed at $112\,\pc$ and $11.2\,\pc$,
respectively.\footnote{This is $2.8$ times the often-quoted
Plummer-equivalent.} The gas softening length is adaptive, but at $z=0$ the
median softening length for gas particles around roughly solar positions
(with cylindrical radii within $500\,\pc$ of $8.2\,\kpc$ and
$\abs{z}<1\,\kpc$) is $98\,\pc$.

We restrict ourselves to the simulation \texttt{m12i} \citep[first introduced
in][]{2016ApJ...827L..23W}. For this work, this galaxy is the best-case
scenario. It does not contain a bar (like \texttt{m12m}) or companion galaxy,
and by eye is the closest to axisymmetric of the three galaxies presented in
\citet{2018arXiv180610564S} \citep{2018MNRAS.481.4133G}.

It is important to remember that simulations of Milky Way-mass galaxies are
not perfect representations of the true Milky Way, as discussed in
\citet{2018arXiv180610564S}. For instance, the velocity structure of
\texttt{m12i} is closer to M31 than the Milky Way. However, in this work we
are most interested in the global properties of the \texttt{m12i} potential,
and specifically in deviations from axisymmetry. From this perspective,
\texttt{m12i} is actually far more axisymmetric than we might expect of the
Milky Way. While \texttt{m12i} has prominent spiral arms, it lacks a bar and
a companion like the Large Magellanic Cloud. In future work, these additional
complications also need to be addressed.

\subsection{Cluster Simulations} \label{ssec:cluster_sim} We simulate a small
star cluster of $256$ stars in the frozen $\z=0$ potential of
$\texttt{m12i}$.

We use the simple tree code
\texttt{pykdgrav}\footnote{\url{https://github.com/omgspace/pykdgrav},
commit:\texttt{fbd1ddc}}.

We use the initial position and velocity of two star particles in
$\texttt{m12i}$

\appendix \section{Appendix 1}
Gonna write an appendix probably
